\def\ColorTheme#1{%
	\ifcase#1%
		dark%
	\or%
		light%
	\or
		success%
	\or%
		info%
	\or%
		warning%
	\or%
		error%
	\or%
		primary%
	\else
		secondary%
	\fi
}
\def\StyleTheme#1{
	\ifcase#1%
		\tcbset{%
			arc=7pt,%
			before upper={\rule[-3pt]{0pt}{10pt}},%
			attach boxed title to top center={yshift=-2mm}%
		}%
	\or%
		\tcbset{%
			attach boxed title to top center={%
				yshift=-0.25mm-\tcboxedtitleheight/2,%
				yshifttext=2mm-\tcboxedtitleheight/2%
			},%
			boxed title style={%
				boxrule=0.5mm,%
				frame code={%
					\path[tcb fill frame] ([xshift=-4mm]frame.west)%
					-- (frame.north west) -- (frame.north east) -- ([xshift=4mm]frame.east)%
					-- (frame.south east) -- (frame.south west) -- cycle; },%
					interior code={ \path[tcb fill interior] ([xshift=-2mm]interior.west)%
					-- (interior.north west) -- (interior.north east)%
					-- ([xshift=2mm]interior.east) -- (interior.south east) -- (interior.south west)%
					-- cycle;%
				}%
			}%
		}%
	\or%
		\tcbset{%
			attach boxed title to top left={xshift=1cm,yshift*=1mm-\tcboxedtitleheight},%
			boxed title style={%
				frame code={%
					\path[fill=tcbcolback!30!black]%
					([yshift=-1mm,xshift=-1mm]frame.north west) arc[start angle=0,end angle=180,radius=1mm]%
					([yshift=-1mm,xshift=1mm]frame.north east) arc[start angle=180,end angle=0,radius=1mm];%
					\path[%
						left color=tcbcolback!60!black,%
						right color=tcbcolback!60!black,%
						middle color=tcbcolback!80!black%
					] ([xshift=-2mm]frame.north west) -- ([xshift=2mm]frame.north east)%
					[rounded corners=1mm]-- ([xshift=1mm,yshift=-1mm]frame.north east)%
					-- (frame.south east) -- (frame.south west)%
					-- ([xshift=-1mm,yshift=-1mm]frame.north west)%
					[sharp corners]-- cycle;%
				},%
				interior engine=empty%
			}%
		}%
	\fi%
}

\NewDocumentEnvironment{ColorThemedBox}{O{0}O{0}om}{
	\def\tmpa{\ColorTheme{#1}}%
	\expandafter\ifx#2\relax\else\StyleTheme{#2}\fi%
	\begin{tcolorbox}[
		enhanced,
		on line,
		colback=palette.\tmpa.back,
		colframe=palette.\tmpa.frame,
		fonttitle=\bfseries,
		colbacktitle=palette.\tmpa.title,
		fonttitle=\bfseries,
		IfValueT={#3}{#3},
		coltext=palette.\tmpa.text,
		boxrule=1pt,
		boxsep=3pt,
		left=6pt,
		right=6pt,
		top=6pt,
		bottom=2pt
	]{#4}%
}{\end{tcolorbox}}

\long\def\ItemArrow#1{\item[\textcolor{palette.dark.frame!90!white}{\faArrowAltCircleRight}] #1}

\newenvironment{Items}{%
	\begin{itemize}
}{%
	\end{itemize}
}

\tcolorboxenvironment{Items}{
    blanker,
    coltext=black,
    borderline west={2.3mm}{0pt}{palette.dark.frame}
}

\NewDocumentCommand{\ColorThemedTCBox}{O{0}m}{%
	\def\tmpa{\ColorTheme{#1}}%
	\tcbox[%
		colback=palette.\tmpa.back,%
		colframe=palette.\tmpa.frame,%
		fonttitle=\bfseries,%
		colbacktitle=palette.\tmpa.title,%
		fonttitle=\bfseries,%
		coltext=palette.\tmpa.text,%
	]{#2}%
}


