\begin{NxSSSBox}[breakable][Clang (LLVM Compiler)]
	\begin{NxIDBox}
		\nxGID{clang} is a modern compiler built on the \nxGID{llvm} framework, offering superior diagnostics, fast compilation times, and extensive support for C language standards.
	\end{NxIDBox}
	\begin{NxIDBoxL}
		\nxTopicD{Overview and History} How Clang emerged as an alternative to GCC and its role in modern development.
		\nxTopicD{Compilation and Optimization} Why Clang is known for its fast compilation times and effective optimization strategies.
		\nxTopicD{Platform Compatibility and Extensions} How Clang supports multiple architectures and compiler-specific features.
		\nxTopicD{Linking Behavior} Linking defines how object files and libraries are combined into an executable, determining dependency management and runtime behavior.
		\nxTopicD{Architecture Specific Settings} Clang provides architecture-specific flags that optimize code generation for different CPUs, ensuring maximum efficiency and compatibility.
		\nxTopicD{Compilation Flags} How Clang enables precise control over compilation warnings, errors, and code standards.
		\nxTopicD{Optimization Levels} Why different levels of Clang optimization impact execution speed, memory usage, and runtime behavior.
		\nxTopicD{Debugging Options} How Clang provides debugging mechanisms to improve runtime analysis and error detection.
		\nxTopicD{Warning Flags} Why Clang’s warning system helps developers catch potential errors and enforce strict coding practices.
		\nxTopicD{Security and Hardening Features} Why enabling security-specific compiler flags mitigates common vulnerabilities.
	\end{NxIDBoxL}
\end{NxSSSBox}

\begin{NxSSSSBox}[breakable][Compilation Flags]
	\begin{NxIDBox}
		Clang provides extensive compilation flags that allow developers to fine-tune error handling, optimizations, debugging, and compliance with various C standards.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-Weverything` flag enables all warnings supported by Clang, helping detect even minor inconsistencies in code.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-fsyntax-only` flag ensures that Clang only checks for syntax errors without compiling the code.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-Wdocumentation` flag checks for incorrect or missing Doxygen-style comments.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-flto` flag enables \nxGID{lto}, improving code efficiency by optimizing across translation units.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-fmodules` flag allows Clang to use modular compilation, speeding up incremental builds.
	\end{NxIDBox}
\end{NxSSSSBox}

\begin{NxSSSSBox}[breakable][Optimization Levels]
	\begin{NxIDBox}
		Clang supports multiple optimization levels, providing a balance between speed, size, and debugging ease.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-Oz` flag optimizes for minimal binary size, making it ideal for embedded systems.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-Ofast` flag enables aggressive optimizations that may break strict standard compliance but improve performance.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-funroll-loops` flag explicitly unrolls loops to reduce iteration overhead.
	\end{NxIDBox}
\end{NxSSSSBox}

\begin{NxSSSSBox}[breakable][Debugging Options]
	\begin{NxIDBox}
		Clang offers additional debugging flags to improve runtime error tracking and execution analysis.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-fsanitize=thread` flag enables ThreadSanitizer, detecting race conditions in multithreaded applications.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-fsanitize=memory` flag helps detect memory access errors.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-fstack-protector-strong` flag provides enhanced stack protection to prevent buffer overflows.
	\end{NxIDBox}
\end{NxSSSSBox}

\begin{NxSSSSBox}[breakable][Security and Hardening Features]
	\begin{NxIDBox}
		Clang includes multiple security-focused compilation flags to enhance binary protection and mitigate exploitation risks.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-ftrapv` flag ensures that signed integer operations trigger runtime traps upon overflow.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-mbranch-protection=pac-ret` flag enforces return address protection on ARM architectures.
	\end{NxIDBox}
	\begin{NxIDBox}
		The `-fsanitize=cfi` flag enables Control Flow Integrity, preventing unintended function pointer hijacking.
	\end{NxIDBox}
\end{NxSSSSBox}

