\newpage
\section{Structures}
\label{Structures}
\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, secA]
	\begin{NexMainBox}[dark, crnA]
		The following functions provide comprehensive utilities for creating, managing, and manipulating structured data like arrays and hashmaps, enabling efficient operations across indexed elements.
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexLink{nx_bijective}{nx_bijective(\NexOption{V}, \NexOption{D1}, \NexOption{D2}, \NexOption{D3})}: Updates a bijective mapping stored in \NexOption{V}, based on three keys (\NexOption{D1}, \NexOption{D2}, \NexOption{D3}). Creates or modifies circular references if all keys are provided, swaps references if two keys are defined, or performs deletions and adjustments based on the keys. Handles edge cases dynamically.}
			\NexItemDark{\NexLink{nx_find_index}{nx_find_index(\NexOption{D1}, \NexOption{S}, \NexOption{D2})}: Searches for the first occurrence of a pattern within a string, with additional constraints. Returns the index of the match or modifies behavior based on optional parameters.}
			\NexItemDark{\NexLink{nx_next_pair}{nx_next_pair(\NexOption{D1}, \NexOption{V1}, \NexOption{V2}, \NexOption{D2}, \NexOption{B1}, \NexOption{B2})}: Retrieves the next pair of start and end indices within a string (\NexOption{D1}), based on associative array delimiters (\NexOption{V1}). Outputs indices and their lengths to the result vector (\NexOption{V2}), while handling escape constraints (\NexOption{D2}). Logic flags (\NexOption{B1}, \NexOption{B2}) control fallback behavior and prioritization during evaluation.}
			\NexItemDark{\NexLink{nx_tokenize}{nx_tokenize(\NexOption{D1}, \NexOption{V1}, \NexOption{S1}, \NexOption{S2}, \NexOption{V2}, \NexOption{D2}, \NexOption{B1}, \NexOption{B2})}: Tokenizes the input string (\NexOption{D1}) into segments based on custom delimiters and pair boundaries. The primary delimiter (\NexOption{S1}, defaulting to a comma) and an optional secondary delimiter (\NexOption{S2}) are used together with a quote map (\NexOption{V2}) and an optional extra pattern (\NexOption{D2}) to drive token separation. Flags (\NexOption{B1} and \NexOption{B2}) control pairing behavior and trimming of tokens, respectively. The found tokens are stored in the array (\NexOption{V1}) with the token count in V1[0].}
			\NexItemDark{\NexLink{nx_vector}{nx_vector(\NexOption{D}, \NexOption{V1}, \NexOption{S}, \NexOption{V2})}: Processes a data string (\NexOption{D}) by tokenizing it into parts using a delimiter (\NexOption{S}) and associative array mappings (\NexOption{V2}). Uses \NexFunction{__nx_quote_map} for initialization and \NexFunction{nx_tokenize} for parsing.}
			\NexItemDark{\NexLink{nx_trim_vector}{nx_trim_vector(\NexOption{D}, \NexOption{V1}, \NexOption{S}, \NexOption{V2})}: Tokenizes a data string (\NexOption{D}) into parts using delimiters and mappings (\NexOption{V2}), then trims each token to remove unnecessary whitespace or characters.}
			\NexItemDark{\NexLink{nx_uniq_vector}{nx_uniq_vector(\NexOption{D}, \NexOption{V1}, \NexOption{S}, \NexOption{V2}, \NexOption{B1}, \NexOption{B2})}: Constructs a unique vector (\NexOption{V1}) from input data (\NexOption{D}), eliminating duplicates, optionally counting occurrences, and leveraging auxiliary vectors (\NexOption{V2}) for processing.}
			\NexItemDark{\NexLink{nx_length}{nx_length(\NexOption{V}, \NexOption{B})}: Calculates the length of elements within a vector (\NexOption{V}) and returns the largest or smallest length based on the logical condition (\NexOption{B}).}
			\NexItemDark{\NexLink{nx_boundary}{nx_boundary(\NexOption{D}, \NexOption{V1}, \NexOption{V2}, \NexOption{B1}, \NexOption{B2})}: Filters elements in a vector (\NexOption{V1}) that match boundary conditions with a given string (\NexOption{D}), and stores the results in another vector (\NexOption{V2}). Provides options to specify matching direction (\NexOption{B1}) and optionally delete the input vector (\NexOption{B2}).}
			\NexItemDark{\NexLink{nx_filter}{nx_filter(\NexOption{D1}, \NexOption{D2}, \NexOption{V1}, \NexOption{V2}, \NexOption{B})}: Filters elements from an input vector (\NexOption{V1}) based on a flexible equality condition (\NexOption{D1}, \NexOption{D2}) and stores the results in an output vector (\NexOption{V2}). Provides an option (\NexOption{B}) to delete the input vector after processing.}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}


\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, secB]
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexLink{nx_option}{nx_option(\NexOption{D}, \NexOption{V1}, \NexOption{V2}, \NexOption{B1}, \NexOption{B2})}: Determines a selected index from an input vector (\NexOption{V1}) based on boundary conditions (\NexOption{D}) and advanced filtering logic. Stores intermediate results in a secondary vector (\NexOption{V2}), applying conditions (\NexOption{B1}, \NexOption{B2}) to refine the output.}
			\NexItemDark{\NexLink{nx_trim_split}{nx_trim_split(\NexOption{D}, \NexOption{V}, \NexOption{S})}: Splits a trimmed input string (\NexOption{D}) into parts stored in a vector (\NexOption{V}), using a customizable delimiter (\NexOption{S}). Defaults to a comma (\texttt{,}) when no delimiter is provided.}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\newpage
\subsection{nx_bijective}
\label{nx_bijective}
\begin{NexCodeBox}{awk}{title={\NexFunction{nx_bijective(\NexOption{V}, \NexOption{D1}, \NexOption{B}, \NexOption{D2})}}}
function nx_bijective(V, D1, D2, D3)
{
	if (D1 != "") {
		if (D2) {
			if (D3 != "") {
				V[D1] = D2
				V[D2] = D3
				V[D3] = D1
			} else {
				V[D1] = D2
				V[D2] = D1
			}
		} else if (D3 != "") {
				V[V[D1]] = D3
			if (D2 != "")
				delete V[D1]
		}
	}
}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
	\begin{NexMainBox}[dark, crnA]
		Updates a bijective mapping stored in \NexOption{V}, based on three keys (\NexOption{D1}, \NexOption{D2}, \NexOption{D3}). Creates or modifies circular references if all keys are provided, swaps references if two keys are defined, or performs deletions and adjustments based on the keys. Handles edge cases dynamically.
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA}
		\begin{NexListDark}
			\NexItemDark{\NexOption{V}: The associative array representing the bijective mapping.}
			\NexItemDark{\NexOption{D1}: The primary key used for mapping and adjustments.}
			\NexItemDark{\NexOption{D2}: The secondary key for mapping relationships. Optional.}
			\NexItemDark{\NexOption{D3}: The tertiary key for creating or modifying circular mappings. Optional.}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\begin{NexCodeBox}{bash}{title={Swap two keys}}
    print nx_bijective(V, "X", "Y", "")
    # Result: V["X"] = "Y", V["Y"] = "X"
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Modify mappings}}
    print nx_bijective(V, "P", 1, "Q")
    # Result: V[V["P"]] = "Q", V["P"] deleted, V["Q"] = V1
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={No operation}}
    print nx_bijective(V, "", "M", "N")
    # Result: (no changes made to V)
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Empty mapping}}
    print nx_bijective(V, "", "", "")
    # Result: (no changes made to V)
\end{NexCodeBox}

\newpage
\subsection{nx_find_index}
\label{nx_find_index}
\begin{NexCodeBox}{bash}{title={\NexFunction{nx_find_index(\NexOption{D1}, \NexOption{S}, \NexOption{D2})}}}
function nx_find_index(D1, S, D2,	f)
{
	if (__nx_defined(D1, 1)) {
		f = 0
		S = __nx_else(S, " ")
		D2 = __nx_else(__nx_defined(D2, 1), "\\\\")
		while (match(D1, S)) {
			f = f + RSTART
			if (! (match(substr(D1, 1, RSTART - 1), D2 "+$") && D2) || int(RLENGTH % 2) == 0)
				break
			f = f + RLENGTH
			D1 = substr(D1, f + 1)
		}
		return f
	}
}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
	\begin{NexMainBox}[dark, crnA]
		Searches for the first match of a given pattern (\NexOption{S}) within a string (\NexOption{D1}) while applying optional constraints (\NexOption{D2}). The function handles fallback conditions and uses nuanced logic to account for escape characters and repeated patterns.
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexOption{D1}: The input string to search.}
			\NexItemDark{\NexOption{S}: The primary pattern to search for. Defaults to the space character (` `).}
			\NexItemDark{\NexOption{D2}: An optional secondary pattern used to constrain matches (e.g., escape sequences). Defaults to the backslash (`\backslash`).}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\begin{NexCodeBox}{bash}{title={Basic pattern matching}}
	D1 = "hell\o world"
	S = "o"
	result = nx_find_index(D1, S)
	# result is 8
	# Explanation: The first occurrence of "o" in "hello world" is excaped, the next occurence is at index 8.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={No match for the pattern}}
	D1 = "hello world"
	S = "z"
	result = nx_find_index(D1, S)
	# result is 0
	# Explanation: Since "z" doesn't exist in the string, the function returns 0.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Default parameters}}
	D1 = "this is an example"
	result = nx_find_index(D1)
	# result is 5
	# Explanation: The default pattern `S` is a space character, and the first space is at index 5.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Complex string with escape sequences}}
	D1 = "path\\to\\file"
	S = "\\\\"
	D2 = "\\\\"
	result = nx_find_index(D1, S, D2)
	# result is 5
	# Explanation: The function navigates the string while respecting escape constraints and finds the first valid match.
\end{NexCodeBox}

\newpage
\subsection{nx_next_pair}
\label{nx_next_pair}
\begin{NexCodeBox}{bash}{title={\NexFunction{nx_next_pair(\NexOption{D1}, \NexOption{V1}, \NexOption{V2}, \NexOption{D2}, \NexOption{B1}, \NexOption{B2})}}}
function nx_next_pair(D1, V1, V2, D2, B1, B2, s, s_l, e, e_l, f, i) {
	if (length(V1) && D1 != "") {
		for (i in V1) {
			if ((f = nx_find_index(D1, i, D2)) && (! s || __nx_if(B2, f > s, f < s))) {
				s = f
				s_l = length(i)
				if (length(V1[i]) && (f = nx_find_index(substr(D1, s + s_l + 1), V1[i], D2))) {
					e = f
					e_l = length(V1[i])
				} else {
					e = ""
					e_l = ""
				}
			}
		}
		if (! s && B1) {
			s = length(D1) + 1
		}
		V2[++V2[0]] = s
		V2[V2[0] "_" s] = s_l
		V2[++V2[0]] = e
		V2[V2[0] "_" e] = e_l
		return V2[0] - 1
	}
}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
	\begin{NexMainBox}[dark, crnA]
		Retrieves the next pair of start and end indices from the input string (\NexOption{D1}) based on specified delimiters (\NexOption{V1}). Stores indices and their lengths in the output vector (\NexOption{V2}) for subsequent operations. Handles escape sequences (\NexOption{D2}) and prioritizes pairs based on logical conditions (\NexOption{B1}, \NexOption{B2}).
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexOption{D1}: The input string to search for start and end pairs.}
			\NexItemDark{\NexOption{V1}: An associative array mapping start delimiters (keys) to end delimiters (values).}
			\NexItemDark{\NexOption{V2}: A vector to store indices and lengths of matched pairs.}
			\NexItemDark{\NexOption{D2}: Constraints for handling escape sequences or specific delimiters.}
			\NexItemDark{\NexOption{B1}: A flag to set a fallback start index if none is found.}
			\NexItemDark{\NexOption{B2}: A logical parameter to prioritize pairs based on index comparison (above or below the previous match).}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\begin{NexCodeBox}{bash}{title={Matching a single pair of delimiters}}
	D1 = "<pair start content end />"
	V1["<pair start"] = "end />"
	V2[0] = 0
	result = nx_next_pair(D1, V1, V2)
	# Result:
	# V2[1] = 1, V2[1_s] = 11
	# V2[2] = 23, V2[2_e] = 6
	# Explanation: Finds the start and end delimiters, capturing their indices and lengths.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Handling fallback start index}}
	D1 = "no delimiters here"
	V1["<start"] = "end />"
	V2[0] = 0
	result = nx_next_pair(D1, V1, V2, "", 1, 0)
	# Result:
	# V2[1] = 21, V2[1_s] = ""
	# V2[2] = "", V2[2_e] = ""
	# Explanation: Sets the fallback start index as the length of D1 + 1 since no match was found.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Multiple pairs with prioritization}}
	D1 = "<startA>contentA<endA><startB>contentB<endB>"
	V1["<startA>"] = "<endA>"
	V1["<startB>"] = "<endB>"
	result = nx_next_pair(D1, V1, V2, "", 0, 1)
	# Result:
	# V2[1] = 1, V2[1_s] = 8
	# V2[2] = 20, V2[2_e] = 7
	# Explanation: Prioritizes pairs based on index comparison and logical conditions.
\end{NexCodeBox}









\newpage
\subsection{nx_tokenize}
\label{nx_tokenize}
\begin{NexCodeBox}{bash}{title={\NexFunction{nx_tokenize(\NexOption{D1}, \NexOption{V1}, \NexOption{S1}, \NexOption{S2}, \NexOption{V2}, \NexOption{D2}, \NexOption{B1}, \NexOption{B2})}}}
function nx_tokenize(D1, V1, S1, S2, V2, D2, B1, B2, v1, v2, c, s, i, l, t) {
    if (D1 != "") {
        if (! length(V2))
            __nx_quote_map(V2)
        S1 = __nx_else(S1, ",")
        V2[S1] = ""
        if (S2) {
            V2[S2] = ""
            nx_bijective(v1, S1, S2)
            c = v1[S1]
        }
        while (D1) {
            i = nx_next_pair(D1, V2, v2, D2, 1, B1)
            t = substr(D1, v2[i], v2[i "_" v2[i]])
            l = v2[i] + v2[i "_" v2[i]]
            s = s substr(D1, 1, v2[i] - 1)
            if (V2[t] == "" || s == D1) {
                s = __nx_if(B2, nx_trim_str(s), s)
                if (S2 && (t in v1 || s == D1)) {
                    if (c == t || s == D1) {
                        if (c == S2)
                            V1[++V1[0]] = s
                        else
                            V1[V1[V1[0]]] = s
                        c = v1[c]
                    } else {
                        V1[++V1[0]] = s
                        if (t == S1 || (s == D1 && c = S1))
                            V1[V1[V1[0]]] = 1
                    }
                } else {
                    V1[++V1[0]] = s
                }
                s = ""
            } else {
                s = s substr(D1, l, v2[++i])
                l = l + v2[i] + v2[i "_" v2[i]]
            }
            D1 = substr(D1, l)
        }
        delete v1
        delete v2
        return V1[0]
    }
}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
    \begin{NexMainBox}[dark, crnA]
        Tokenizes an input string (\NexOption{D1}) into multiple segments by finding token boundaries using a customizable delimiter setup.  
        The primary delimiter (\NexOption{S1}) defaults to a comma (via __nx_else), and if a secondary delimiter (\NexOption{S2}) is provided, a reciprocal mapping is created using nx_bijective.  
        A mapping array (\NexOption{V2}) – automatically populated by __nx_quote_map if empty – drives pair-based token detection (via nx_next_pair).  
        Depending on the flag (\NexOption{B2}), tokens are optionally trimmed (using nx_trim_str), and the tokens are stored in the array (\NexOption{V1}) with the count in V1[0].
    \end{NexMainBox}
    \begin{NexMainBox}[dark, crnA]
        \begin{NexListDark}
            \NexItemDark{\NexOption{D1}: The input string to be tokenized.}
            \NexItemDark{\NexOption{V1}: An array (destination table) in which tokens are accumulated; V1[0] holds the token count.}
            \NexItemDark{\NexOption{S1}: The primary delimiter (defaults to "," if not provided).}
            \NexItemDark{\NexOption{S2}: An optional secondary delimiter for creating bidirectional token mappings.}
            \NexItemDark{\NexOption{V2}: A mapping array for quotes/delimiters; if empty, it's populated by __nx_quote_map.}
            \NexItemDark{\NexOption{D2}: An optional pattern used in token boundary detection.}
            \NexItemDark{\NexOption{B1}: A flag passed on to nx_next_pair for controlling pairing behavior.}
            \NexItemDark{\NexOption{B2}: A flag that, when true, applies trimming to tokens via nx_trim_str.}
        \end{NexListDark}
    \end{NexMainBox}
\end{NexMainBox}




\begin{NexCodeBox}{bash}{title={Basic tokenization with comma}}
    # Suppose V1 and V2 are pre-declared (e.g., V1 = [] and V2 = [])
    print nx_tokenize("apple,banana,cherry", V1, ",", "", V2, "", 0, 0)
    # Expected Result: 3
    # Where V1[1] = "apple", V1[2] = "banana", V1[3] = "cherry"
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Tokenization with trimming}}
    # Here B2 is set to 1 (true) so that leading/trailing spaces are trimmed.
    print nx_tokenize("  dog , cat ,  bird  ", V1, ",", "", V2, "", 0, 1)
    # Expected Result: 3
    # With trimmed tokens: V1[1] = "dog", V1[2] = "cat", V1[3] = "bird"
\end{NexCodeBox}

\newpage
\subsection{nx_length}
\label{nx_length}
\begin{NexCodeBox}{bash}{title={\NexFunction{nx_length(\NexOption{V}, \NexOption{B})}}}
function nx_length(V, B,	i, j, k)
{
	if (length(V) && 0 in V) {
		for (i = 1; i <= V[0]; i++) {
			j = length(V[i])
			if (! k || __nx_if(B, k < j, k > j))
				k = j
		}
		return int(k)
	}
}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
	\begin{NexMainBox}[dark, crnA]
		Calculates the length of elements within an input vector (\NexOption{V}) and determines the largest or smallest length based on a given logical condition (\NexOption{B}).
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexOption{V}: The input vector containing elements whose lengths need to be evaluated.}
			\NexItemDark{\NexOption{B}: A logical flag that determines whether to return the smallest length (if `false`) or the largest length (if `true`).}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\begin{NexCodeBox}{bash}{title={Finding the largest length}}
	V[0] = 3
	V[1] = "short"
	V[2] = "longer"
	V[3] = "lengthiest"
	B = 1
	result = nx_length(V, B)
	# Result: 10
	# Explanation: Evaluates the lengths of elements in V and returns the largest value, which is 10 (from "lengthiest").
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Finding the smallest length}}
	V[0] = 3
	V[1] = "short"
	V[2] = "longer"
	V[3] = "lengthiest"
	B = 0
	result = nx_length(V, B)
	# Result: 5
	# Explanation: Evaluates the lengths of elements in V and returns the smallest value, which is 5 (from "short").
\end{NexCodeBox}

\newpage
\subsection{nx_boundary}
\label{nx_boundary}
\begin{NexCodeBox}{bash}{title={\NexFunction{nx_boundary(\NexOption{D}, \NexOption{V1}, \NexOption{V2}, \NexOption{B1}, \NexOption{B2})}}}
function nx_boundary(D, V1, V2, B1, B2,	 i)
{
	if (length(V) && 0 in V && D != "") {
		for (i = 1; i <= V1[0]; i++) {
			if (__nx_if(B1, V1[i] ~ D "$", V1[i] ~ "^" D))
				V2[++V2[0]] = V1[i]
		}
		if (B2)
			delete V1
		return V2[0]
	}
}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
	\begin{NexMainBox}[dark, crnA]
		Filters elements from an input vector (\NexOption{V1}) that match the boundary conditions specified by a string (\NexOption{D}). Results are stored in an output vector (\NexOption{V2}), with the option to prioritize start or end boundary matching (\NexOption{B1}). The function can optionally delete the input vector (\NexOption{B2}) after processing.
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexOption{D}: The string used to define boundary conditions for filtering elements.}
			\NexItemDark{\NexOption{V1}: The input vector containing elements to be filtered.}
			\NexItemDark{\NexOption{V2}: The output vector to store elements matching the boundary conditions.}
			\NexItemDark{\NexOption{B1}: A logical flag to specify boundary matching. If `true`, matches elements ending with (\NexOption{D}); if `false`, matches elements starting with (\NexOption{D}).}
			\NexItemDark{\NexOption{B2}: A flag to delete the input vector (\NexOption{V1}) after filtering, if set to `true`.}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\begin{NexCodeBox}{bash}{title={Filtering elements ending with a boundary}}
	V1[1] = "boundary_end"
	V1[2] = "no_match"
	V1[3] = "another_end"
	D = "end"
	B1 = 1
	nx_boundary(D, V1, V2, B1, 0)
	# Result:
	# V2[1] = "boundary_end"
	# V2[2] = "another_end"
	# Explanation: Filters elements in V1 that end with "end" and stores them in V2.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Filtering elements starting with a boundary}}
	V1[1] = "start_boundary"
	V1[2] = "no_match"
	V1[3] = "start_another"
	D = "start"
	B1 = 0
	nx_boundary(D, V1, V2, B1, 0)
	# Result:
	# V2[1] = "start_boundary"
	# V2[2] = "start_another"
	# Explanation: Filters elements in V1 that start with "start" and stores them in V2.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Deleting the input vector after filtering}}
	V1[1] = "boundary_delete"
	V1[2] = "no_match"
	V1[3] = "delete_end"
	D = "delete"
	B1 = 1
	B2 = 1
	nx_boundary(D, V1, V2, B1, B2)
	# Result:
	# V2[1] = "delete_end"
	# V1: Cleared
	# Explanation: Filters elements in V1 matching the boundary condition "delete" (ending with "delete"), stores "delete_end" in V2, and clears V1 after processing due to B2 being set to true.
\end{NexCodeBox}

\newpage
\subsection{nx_filter}
\label{nx_filter}
\begin{NexCodeBox}{bash}{title={\NexFunction{nx_filter(\NexOption{D1}, \NexOption{D2}, \NexOption{V1}, \NexOption{V2}, \NexOption{B})}}}
function nx_filter(D1, D2, V1, V2, B,   i, v1, v2)
{
	if (length(V1) && 0 in V1) {
		for (i = 1; i <= V1[0]; i++) {
			if (__nx_equality(D1, D2, V1[i]))
				V2[++V2[0]] = V1[i]
		}
		if (B)
			delete V1
		return V2[0]
	}
}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
	\begin{NexMainBox}[dark, crnA]
		Filters elements from an input vector (\NexOption{V1}) based on a flexible equality condition defined by (\NexOption{D1}) and (\NexOption{D2}). Matching elements are appended to an output vector (\NexOption{V2}). The function supports optional deletion of the input vector (\NexOption{V1}) after filtering to optimize memory usage.
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexOption{D1}: The primary value or pattern used for comparison.}
			\NexItemDark{\NexOption{D2}: The secondary value or pattern used to refine the comparison.}
			\NexItemDark{\NexOption{V1}: The input vector containing elements to be filtered.}
			\NexItemDark{\NexOption{V2}: The output vector to store elements that meet the equality condition.}
			\NexItemDark{\NexOption{B}: A flag to delete the input vector (\NexOption{V1}) after processing if set to `true`.}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\begin{NexCodeBox}{bash}{title={Filtering elements with a simple equality condition}}
	V1[1] = "apple"
	V1[2] = "orange"
	V1[3] = "apple"
	D1 = "apple"
	D2 = "="
	nx_filter(D1, D2, V1, V2, 0)
	# Result:
	# V2[1] = "apple"
	# V2[2] = "apple"
	# Explanation: Filters elements in V1 that are equal to "apple" and stores them in V2.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Filtering elements with a numeric condition}}
	V1[1] = 10
	V1[2] = 20
	V1[3] = 30
	D1 = 15
	D2 = ">"
	nx_filter(D1, D2, V1, V2, 0)
	# Result:
	# V2[1] = 20
	# V2[2] = 30
	# Explanation: Filters elements in V1 greater than 15 and stores them in V2.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Deleting the input vector after filtering}}
	V1[1] = "match"
	V1[2] = "no_match"
	V1[3] = "match"
	D1 = "match"
	D2 = "="
	B = 1
	nx_filter(D1, D2, V1, V2, B)
	# Result:
	# V2[1] = "match"
	# V2[2] = "match"
	# V1: Cleared
	# Explanation: Filters elements in V1 that match "match", stores them in V2, and clears V1 after processing.
\end{NexCodeBox}

\newpage
\subsection{nx_option}
\label{nx_option}
\begin{NexCodeBox}{bash}{title={\NexFunction{nx_option(\NexOption{D}, \NexOption{V1}, \NexOption{V2}, \NexOption{B1}, \NexOption{B2})}}}
function nx_option(D, V1, V2, B1, B2,   i, v1)
{
	if (length(V1) && 0 in V1) {
		if (nx_boundary(D, V1, v1, B1) > 1) {
			if (nx_filter(nx_append_str("0", nx_length(v1, B2)), "=_", v1, V2, 1) == 1) {
				i = V2[1]
				delete V2
				return i
			}
		} else {
			i = v1[1]
			delete v1
			return i
		}
	}
}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
	\begin{NexMainBox}[dark, crnA]
		Selects a string from an input vector (\NexOption{V1}) that matches boundary conditions (\NexOption{D}) and additional logic refinements. The function processes intermediate results using a secondary vector and logical conditions, enabling flexible selection criteria.
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexOption{D}: A string or pattern used as a boundary condition for selection.}
			\NexItemDark{\NexOption{V1}: The primary input vector containing elements to evaluate.}
			\NexItemDark{\NexOption{V2}: A secondary vector used for intermediate filtering results.}
			\NexItemDark{\NexOption{B1}: A logical flag controlling boundary matching (e.g., start or end).}
			\NexItemDark{\NexOption{B2}: A logical flag influencing the filtering length criteria during refinement.}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\begin{NexCodeBox}{bash}{title={Selecting a string based on boundary conditions}}
	V1[1] = "start_option"
	V1[2] = "middle_match"
	V1[3] = "end_option"
	V1[0] = 3 # This was populated dynamically earlier
	D = "option"
	B1 = 1
	B2 = 1
	result = nx_option(D, V1, V2, B1, B2)
	# Result: "end_option"
	# Explanation: Filters V1 for elements matching the boundary condition "option" at the end and returns the matching string ("end_option").
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Returning a single matching string}}
	V1[1] = "single_match"
	V1[2] = "no_match"
	V1[0] = 2 # Populated dynamically via earlier functions
	D = "single"
	B1 = 0
	B2 = 1
	result = nx_option(D, V1, V2, B1, B2)
	# Result: "single_match"
	# Explanation: Matches "single_match" based on the boundary condition "single" at the start and returns the matching string.
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={No valid boundary match}}
	V1[1] = "no_boundary"
	V1[2] = "no_match"
	V1[0] = 2 # Managed dynamically by earlier functions
	D = "option"
	B1 = 0
	B2 = 0
	result = nx_option(D, V1, V2, B1, B2)
	# Result: None
	# Explanation: No elements in V1 match the boundary condition "option", so the function returns no result.
\end{NexCodeBox}

\newpage
\subsection{nx_trim_split}
\label{nx_trim_split}
\begin{NexCodeBox}{bash}{title={\NexFunction{nx_trim_split(\NexOption{D}, \NexOption{V}, \NexOption{S})}}}
	function nx_trim_split(D, V, S) {
		return split(nx_trim_str(D), V, "[ \v\t\n\f]*" __nx_else(S, ",") "[ \v\t\n\f]*")
	}
\end{NexCodeBox}

\begin{NexMainBox}[light, hdrA, sdwA, crnA, grwB, ssecB]
	\begin{NexMainBox}[dark, crnA]
		Splits a trimmed input string (\NexOption{D}) into parts stored in a vector (\NexOption{V}), using a customizable delimiter (\NexOption{S}). Defaults to a comma (\texttt{,}) when no delimiter is provided.
	\end{NexMainBox}
	\begin{NexMainBox}[dark, crnA]
		\begin{NexListDark}
			\NexItemDark{\NexOption{D}: The input string to be trimmed and split.}
			\NexItemDark{\NexOption{V}: The vector where split segments are stored.}
			\NexItemDark{\NexOption{S}: The delimiter used for splitting. Defaults to a comma (\texttt{,}) if not provided.}
		\end{NexListDark}
	\end{NexMainBox}
\end{NexMainBox}

\begin{NexCodeBox}{bash}{title={Splitting with a custom delimiter}}
	D = "apple ; orange ; banana"
	S = ";"
	result = nx_trim_split(D, V, S)
	# Result: V[1] = "apple", V[2] = "orange", V[3] = "banana"
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Default delimiter}}
	D = "apple,orange,banana"
	S = ""
	result = nx_trim_split(D, V, S)
	# Result: V[1] = "apple", V[2] = "orange", V[3] = "banana"
\end{NexCodeBox}

\begin{NexCodeBox}{bash}{title={Whitespace trimming}}
	D = "  apple  ; orange ;   banana   "
	S = ";"
	result = nx_trim_split(D, V, S)
	# Result: V[1] = "apple", V[2] = "orange", V[3] = "banana"
\end{NexCodeBox}

