\nxSections{Databases}{2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nxSections{CREATE DATABASE — Syntax Across Engines}{3}
\begin{NxCodeBox}{sql}{title={\textbf{Creating a Customized Database}
        \begin{NxDarkList}
                \nxEachLabel{DBSecondary}{Tertiary}{{1}{43}}{%
                        {custom_app_db}/{Tailored for multilingual support, user ownership, and connection limits.},%
                        {database creation}/{Defines encoding, collation, owner, and other engine-specific options.}
                }
        \end{NxDarkList}
}}

-- PostgreSQL
CREATE DATABASE custom_app_db
WITH 
    OWNER = app_admin,
    ENCODING = 'UTF8',
    LC_COLLATE = 'en_US.UTF-8',
    LC_CTYPE = 'en_US.UTF-8',
    TABLESPACE = pg_default,
    CONNECTION LIMIT = 50;

-- MariaDB / MySQL
CREATE DATABASE IF NOT EXISTS custom_app_db
DEFAULT CHARACTER SET = utf8mb4
DEFAULT COLLATE = utf8mb4_unicode_ci
COMMENT = 'Multilingual app database';

-- SQLite3
-- No CREATE DATABASE command; database is created by opening a new file
-- Example (from client or script):
.open custom_app_db.sqlite
-- Collation and encoding are handled internally; no explicit options
\end{NxCodeBox}

\begin{NxLightListBox}[title={CREATE DATABASE — The Ritual of Customized Initialization}]
        \nxEachLabel{ArrowDark}{Secondary}{{1}{43}}{%
                {Purpose}/{Initializes a new database with specific encoding, collation, ownership, and connection rules},%
                {Input}/{\nxLnArcBox[]{CREATE DATABASE name WITH options}},%
                {Fallback}/{Defaults are applied if options are omitted; may affect performance or compatibility},%
                {Rendering}/{Options influence storage behavior, character support, and access control},%
                {Use Case}/{Used when deploying multilingual apps, enforcing quotas, or isolating schema ownership}
        }
\end{NxLightListBox}

\begin{NxLightBox}[title={CREATE DATABASE — Syntax Glyph Map}]
        \begin{tabularx}{\textwidth}{|l|X|}
                \hline
                \textbf{Engine} & \textbf{CREATE DATABASE Support} \\
                \hline
                PostgreSQL & {\nxCheckSuccess} supports OWNER, ENCODING, COLLATE, CONNECTION LIMIT, TABLESPACE, TEMPLATE, and more \\
                MariaDB / MySQL & {\nxCheckSuccess} supports CHARACTER SET, COLLATE, COMMENT, and IF NOT EXISTS \\
                SQLite3 & {\nxCheckSuccess} creates database by opening a file; no SQL options supported \\
                \hline
                \textbf{Engine} & \textbf{CREATE DATABASE Behavior} \\
                \hline
                PostgreSQL & Initializes catalog with locale and encoding; enforces ownership and connection limits \\
                MariaDB / MySQL & Creates schema folder with charset and collation metadata; COMMENT stored in system tables \\
                SQLite3 & Creates file-based database; encoding is UTF-8 by default; no schema-level customization \\
                \hline
        \end{tabularx}
\end{NxLightBox}

\begin{NxLightListBox}[title={CREATE DATABASE — Beginner Questions}]
        \nxEachLabel{ArrowDark}{Secondary}{{1}{43}}{%
                {What does ENCODING do?}/{It defines the character set used to store text — UTF8 is common for multilingual support.},%
                {What is LC_COLLATE and LC_CTYPE?}/{They control sorting and character classification based on locale.},%
                {Can I limit connections?}/{Yes — PostgreSQL supports \nxLnArcBox[]{CONNECTION LIMIT}.},%
                {What does COMMENT do in MariaDB?}/{It adds a description to the database for documentation or metadata.},%
                {Does SQLite support these options?}/{No — it uses defaults and does not expose database-level configuration.},%
                {Is OWNER required?}/{No — but assigning ownership helps manage privileges and schema isolation.}
        }
\end{NxLightListBox}

