\begin{ColorThemedBox}[1][2][title=Programming]\relax
	\ShowSvgBox{0}{%
		 ../lib/svg/latex.svg,
		 ../lib/svg/vim.svg,
		 ../lib/svg/cpp.svg,
		 ../lib/svg/java.svg,
		 ../lib/svg/lua.svg,
		 ../lib/svg/awk.svg,
		 ../lib/svg/bash.svg,
		 ../lib/svg/perl.svg,
		 ../lib/svg/tex.svg,
		 ../lib/svg/python.svg,
		 ../lib/svg/php.svg,
		 ../lib/svg/ruby.svg,
		 ../lib/svg/c.svg
	}
	\begin{Items}
		\ItemArrow{\bftext{C:} Extensive experience in developing efficient and optimized code for system programming, embedded systems, and performance-critical applications.}%
		\ItemArrow{\bftext{C++:} Skilled in using C++ for both system-level programming and application development in game development and real-time simulation.}%
		\ItemArrow{\bftext{Java:} Proficient in building robust, scalable enterprise applications, Android apps, and web applications.}%
		\ItemArrow{\bftext{Python:} Adept at utilizing Python for web development, data science, machine learning, automation, and scripting.}%
		\ItemArrow{\bftext{Perl:} Experienced in scripting, text parsing, and system automation, with strong text processing capabilities.}%
		\ItemArrow{\bftext{PHP:} Skilled in backend web development, creating dynamic web pages, and integrating with databases.}%
		\ItemArrow{\bftext{Ruby:} Proficient in web application development using Ruby on Rails, scripting, and automation.}%
		\ItemArrow{\bftext{Bash:} Experienced in writing scripts for system automation and task management.}%
		\ItemArrow{\bftext{AWK:} Skilled in data processing, pattern scanning, and scripting for data extraction and reporting.}%
		\ItemArrow{\bftext{Lua:} Experienced in scripting for game development, embedded systems, and extending applications.}%
		\ItemArrow{\bftext{TeX/LaTeX:} Proficient in using LaTeX for academic and technical writing, creating complex documents with mathematical content.}%
		\ItemArrow{\bftext{Vim Script:} Skilled in writing Vim scripts to customize and extend the functionality of Neovim/Vim, creating custom plugins and configurations.}%
	\end{Items}
\end{ColorThemedBox}
\\

