\begin{NexColorBox}[color=1, style=2, title=Tools and Technologies]\relax
	\ShowSvgBox{0}{%
		../lib/svg/git.svg,%
		../lib/svg/docker.svg,%
		../lib/svg/podman.svg%
	}
	\begin{Items}
		\ItemArrow{\bftext{Neovim:} Skilled in configuring and customizing Neovim with Lua and Vim script to enhance productivity and streamline development workflows.}%
		\ItemArrow{\bftext{Git:} Experienced in using Git for source code management, branching, merging, and collaboration in a team environment.}%
		\ItemArrow{\bftext{Docker:} Proficient in creating, managing, and deploying Docker containers. Experienced in writing Dockerfiles and managing Docker Compose files.}%
		\ItemArrow{\bftext{Podman:} Skilled in using Podman for container lifecycle management, including building, running, and pushing containers.}%
		\ItemArrow{\bftext{runc:} Experienced in using runc as a container runtime for running and managing containers.}%
		\ItemArrow{\bftext{containerd:} Proficient in using containerd for container orchestration and management within Kubernetes clusters.}%
		\ItemArrow{\bftext{iproute2:} Skilled in using iproute2 tools for network configuration, routing, and traffic shaping.}%
		\ItemArrow{\bftext{nftables:} Experienced in using nftables for creating complex firewall rules and managing network security.}%
		\ItemArrow{\bftext{Extended Berkeley Packet Filter (eBPF):} Skilled in using eBPF for network performance analysis, monitoring, and enhancing security.}%
		\ItemArrow{\bftext{Buildah:} Proficient in using Buildah to create and manage container images, ensuring security and compliance.}%
		\ItemArrow{\bftext{crun:} Experienced in using crun as a container runtime to efficiently manage containerized.}%
	\end{Items}
\end{NexColorBox}
\smallskip

