\begin{ColorThemedBox}[1][2][title=Work Experience]\relax
	\begin{ColorThemedBox}[0][2]\relax
		\faUser\hspace{10pt}IT Assistant to a Doctoral Researcher\par\smallskip
		\faLocationArrow\hspace{10pt}University of Sheffield, Sheffield, South Yorkshire, England\par\smallskip
	\end{ColorThemedBox}
	\begin{Items}
		\ItemArrow{Provided technical support and assistance to a doctoral researcher, ensuring smooth operation of computing resources and research tools.}
		\ItemArrow{Assisted in setting up and maintaining hardware, software, and network configurations.}
		\ItemArrow{Developed and implemented scripts to automate repetitive tasks, improving overall efficiency.}
		\ItemArrow{Troubleshot technical issues and resolved them promptly to minimize disruption to the research process.}
		\ItemArrow{Collaborated with the researcher to ensure data integrity and security during the research project.}
	\end{Items}
	\begin{ColorThemedBox}[0][2]\relax
		\faUser\hspace{10pt}Instructor\par\smallskip
		\faLocationArrow\hspace{10pt}Canterbury Recreation Complex, Ottawa, Ontario, Canada\par\smallskip
	\end{ColorThemedBox}
	\begin{Items}
		\ItemArrow{Designed and delivered engaging and informative lessons for students ranging from beginners to level 9.}
		\ItemArrow{Created customized lesson plans to meet the diverse needs and skill levels of students.}
		\ItemArrow{Utilized a variety of teaching methods and tools to facilitate learning and keep students motivated.}
		\ItemArrow{Monitored student progress and provided constructive feedback to help them improve their skills.}
		\ItemArrow{Organized and conducted practical sessions, demonstrations, and hands-on activities to enhance learning experiences.}
		\ItemArrow{Fostered a supportive and inclusive learning environment to encourage student participation and engagement.}
		\ItemArrow{Collaborated with other instructors and staff to ensure a consistent and high-quality learning experience for all students.}
	\end{Items}
\end{ColorThemedBox}
\\

