\begin{NxSBox}[][History of C]
    \begin{NxIDBox}
        The history of C is closely tied to the evolution of computing and software development. This section explores its origins, major milestones, and continued influence on modern programming.
    \end{NxIDBox}
    \begin{NxIDBoxL}
        \nxTopicD{ssec:Origins and Development}{Origins and Development} C was created as an improvement over existing languages, particularly assembly, \nxGID{algol}, and \nxGID{bcpl}, to provide better portability and structure.
    \end{NxIDBoxL}
    \begin{NxIDBoxL}
        \nxTopicD{ssec:Evolution Through Standards}{Evolution Through Standards} Over the years, C has evolved through official standards such as C89, C99, C11, and C17, each refining features and improving compatibility across platforms.
    \end{NxIDBoxL}
\end{NxSBox}

\begin{NxSSBox}[][Origins and Development]
    \begin{NxIDBox}
        The development of C was driven by the need for a flexible, efficient, and portable programming language that could be used for system programming and application development.
    \end{NxIDBox}
    \begin{NxIDBoxL}
        \nxTopicD{sssec:Assembly to Structured Programming}{From Assembly to Structured Programming} Before C, programmers relied on assembly, which was efficient but lacked portability and structure.
    \end{NxIDBoxL}
    \begin{NxIDBoxL}
        \nxTopicD{sssec:Dennis Ritchie’s Role}{Dennis Ritchie’s Role in C’s Birth} Dennis \nxGID{ritchie} developed C at \nxGID{bell_labs} to provide a balance between low-level control and structured programming.
    \end{NxIDBoxL}
\end{NxSSBox}

\begin{NxSSSBox}[][Assembly to Structured Programming]
    \begin{NxIDBox}[title={Limitations of Assembly}]
        Assembly language allowed direct hardware manipulation, but its complexity made programming tedious, with poor readability and lack of portability.
    \end{NxIDBox}
    \begin{NxIDBox}[title={Influence of ALGOL and BCPL}]
        Early high-level languages like \nxGID{algol} and \nxGID{bcpl} introduced structured programming, which influenced the development of C.
    \end{NxIDBox}
\end{NxSSSBox}

\begin{NxSSSSBox}[][Limitations of Assembly]
    \begin{NxIDBox}[title={Challenges in Portability}]
        Code written in assembly was tightly linked to specific hardware architectures, making it difficult to adapt software across different systems.
    \end{NxIDBox}
    \begin{NxIDBox}[title={Complexity in Debugging}]
        Assembly programs required detailed memory management, making debugging significantly harder compared to structured programming languages.
    \end{NxIDBox}
\end{NxSSSSBox}

\input{./contents/nex-c/introduction.d/history.d/origin.tex}

