\section{Components}
\label{sec:component}
The \sTE{run.sh} script initiates the POSIX Nexus daemon, which encompasses the following functionalities:
\bigskip
\begin{baseBoxOne}{}{dark}
    \begin{posnexItemize}
        \item[\sA] \sE{Database Management}: Efficiently handles data storage and retrieval to support various applications.
        \item[\sA] \sE{SSH Authentication}: Secures connections using SSH keys to ensure only authorized access.
        \item[\sA] \sE{Command Distribution}: Distributes commands across specified Nexuses, enabling coordinated execution.
        \item[\sA] \sE{Web Server Functionalities}: Provides web server capabilities akin to Cockpit, applicable to any system, not limited to \sTE{systemd}.
        \item[\sA] \sE{Comprehensive Security Measures}: Ensures secure information sharing among Nexuses and connected machines via multicast groups, authenticated through SSH keys.
        \item[\sA] \sE{Interactive Menu}: Manages IP addresses of child machines, enabling secure connections through public keys.
        \item[\sA] \sE{Dual Authentication Mechanism}: Ensures both Nexus and group member validation, with automatic ejection of any machine posing a security risk detected by multiple systems.
    \end{posnexItemize}
\end{baseBoxOne}
\bigskip
The POSIX Nexus aims to create a robust network that prioritizes security without compromising usability.
Routine tasks are handled via \sTE{awk}, while advanced features are developed using the \sTE{C90} standard library.
This approach ensures efficient script execution and consistent performance across various systems.

\input{sections/components/00-structure.tex}

\input{sections/components/01-exceptions.tex}

\input{sections/components/02-strings.tex}

\input{sections/components/03-miscelanious.tex}

\input{sections/components/04-Input-output.tex}

\input{sections/components/05-networking.tex}

\input{sections/components/06-data-structires.tex}

\input{sections/components/07-security.tex}

\input{sections/components/08-system-operations.tex}
